% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jintao Ye}

\basicInfo{
  \email{keys961@hotmail.com} \textperiodcentered\
  \phone{(+86) 188-6715-0382} \textperiodcentered\ 
  \linkedin[Jintao Ye]{https://www.linkedin.com/in/\%E9\%87\%91\%E9\%9F\%AC-\%E5\%8F\%B6-9aa07470/}
}

\section{Education}
\datedsubsection{\textbf{Zhejiang University}, Hangzhou, China}{2019 -- Present}
Candidate for \textit{M.Eng.} in Computer Technology, expected March 2022
\datedsubsection{\textbf{Zhejiang University}, Hangzhou, China}{2015 -- 2019}
\textit{B.E.} in Software Engineering

\section{Work Experience}
\datedsubsection{\textbf{Zhejiang Bangsun Technology Co., Ltd}}{Aug. 2018 -- Present}
\role{Intern}{Software Engineer}
\begin{enumerate}
  \item \textbf{Cube Base: A Distributed KV Storage for Stream Cube} (Dec. 2018 -- Present)
  \begin{itemize}
    \item Implemented off-heap in-memory key-value storage, supporting secondary key-value for Cube Base
    \item Implemented the secondary index to accelerate the scan operation
    \item Implemented data sharding based on the node's hardware infomation
    \item Implemented cluster management with ZooKeeper
    \item Implemented automatic data migration after cluster reconfiguration
    \item Implemented pipelined, asynchronized and merged master-slave replication
    \item Implemented data dump, binlog and replication catch-up for data consistency and availability
    \item After integrated with Stream Cube:
    \begin{itemize}
      \item Disable replication: throughput increased by 15.4\% and 100.8\% compared with Aerospike and Redis Cluster respectively
      \item Enable replication: throughput increased by 3.7\% and 66.1\% compared with Aerospike and Redis Cluster respectively
    \end{itemize}
  \end{itemize}
  \item \textbf{Graph Cube: An Aggregated Graph Query Module on Stream Cube} (Apr. 2019 -- Jul. 2019)
  \begin{itemize}
    \item Defined a query language based on Cypher
    \item Implemented intermediate representation layer from the parsed information by ANTRL4
    \item Optimized query performance by enabling batch query on fan-out edges
  \end{itemize}
  \item \textbf{Peng Cheng Laboratory: A Streaming System of Security Pattern Matching} (Mar. 2020 -- Jun. 2020)
  \begin{itemize}
    \item Implemented security pattern registration and management by Kafka and MySQL
    \item Implemented approximate deduplication for the incoming security event stream
    \item Implemented phishing, sprear-phishing, waterhole, botnet and DDoS pattern matching by Kafka Stream and Cube Base
    \item Supported at least 10,000 pattern matching tasks within 2 ms delay
    \item Supported horizontal scaling for parallel processing
  \end{itemize}
\end{enumerate}

\datedsubsection{\textbf{Hangzhou Qunhe Infomation Technology Co., Ltd (Kujiale)}}{Mar. 2018 -- Jun. 2018}
\role{Intern}{Backend Software Engineer}
Responsible for the development and maintenance of the floor plan figure generation.
\begin{itemize}
  \item Fixed logic and calculation bugs of figure rendering
  \item Implemented a new version of the floor plan figure
  \item Refactored the project with micro-task framework and decoupled the rendering service and the upper REST services
  \item Optimized the cache layer to solve the Full-GC problem
\end{itemize}

\newpage

\section{Project}
\datedsubsection{\textbf{influx-proxy}}{Sept. 2020 -- Oct. 2020}
\role{Go}{Individual Project}
A proxy for InfluxDB based on Eleme. influx-proxy. https://github.com/keys961/influx-proxy
\begin{itemize}
  \item Removed the dependency of Redis
  \item Optimized the route strategy for query requests
  \item Supported non-measurement-crossing queries with SELECT/SHOW/DELETE clauses.
\end{itemize}
\datedsubsection{\textbf{MiniSQL}}{May 2017 -- Jun. 2017}
\role{C++}{Individual Project}
A simple relational DBMS implementation. https://github.com/keys961/MiniSql
\begin{itemize}
  \item Implemented buffer management, applied with FIFO page replacement
  \item Implemented B+ tree to build the index
  \item Implemented record and catalog management
  \item Supported simple SQL execution on a single table
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{Skills and Interests}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java > C/C++/Go/Rust
  \item Platform: Linux
  \item Frameworks: Spring Boot, Netty, RSocket, Redis, Kafka
  \item Development: Web, Disrtibuted System
  \item Interests: Distributed System, Stream Processing 
\end{itemize}

\section{Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://keys961.github.io
  \item GitHub: https://github.com/keys961
  \item Languages: English - Fluent(CET-6), Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
